\begin{coverpages}
    \begin{center}
	\LARGE\textbf{\fullcoursename} 
	\huge{\textbf{\assignment}} \\
	\LARGE{\textbf{Writeup Due: }\due} \\
    \LARGE{\textbf{Checkoffs Due: }\demosdue} \\
	\end{center}
	\begin{tabular}{ll}
		Name: &\rule{0.83\textwidth}{0.4pt} \bigskip \\ 
		Andrew ID: &\rule{0.83\linewidth}{0.4pt} \\
	\end{tabular}

	\medbreak
	\textbf{\large How to submit labs:} 
	
	Download from this file from \emph{Canvas} and edit it with whatever PDF editor you're most comfortable with. Some recommendations from other students and courses that use Gradescope include:
	\vspace{-1\baselineskip}
	\begin{description}[leftmargin=12em,style=nextline,itemsep=0em]

        \item[\href{https://dochub.com/}{DocHub}] An online PDF annotator that works on desktop and mobile platforms.
 
        \item[\href{https://www.pdfescape.com/}{pdfescape.com}] A web-based PDF editor that works on most, if not all, devices. 
		\item[\href{https://www.iannotate.com/}{iAnnotate}] A cross-platform editor for mobile devices (iOS/Android). 
	\end{description}
	\vspace{-1\baselineskip}
	
	\textit{If you have difficulties inserting your image into the PDF, simply append them as an extra page to the END of your lab packet and mark the given box. \textbf{Do NOT insert between pages.}}
	
	If you'd prefer not to edit a PDF, you can print the document, write your answers in neatly and scan it as a PDF. \emph{(Note: We do not recommend this as unreadable lab reports will not be graded!)}. Once you've completed the lab, upload and submit it to \textit{Gradescope}. 
	
	Note that while you may work with other students on completing the lab, this writeup is to be completed alone. Do not exchange or copy measurements, plots, code, calculations, or answer in the lab writeup.
	
	\textbf{\large Your lab grade will consist of two components:}
	\vspace{-\baselineskip}
	\begin{enumerate}
	    \itemsep0pt
		\item Answers to all lab questions in your lab handout. The questions consist of measurements taken during the lab activities, calculations on those measurements and questions on the lab material.
		\item A demonstration of your working lab circuits and conceptual understanding of the material. This demo will occur during office hours.
	\end{enumerate}
    \vspace{-.25cm}
	\begin{center}
		\partialgradetable{credit}[h][questions]
	\end{center}
	\vfill
\end{coverpages}
\pagebreak